Multi-stage programming with functors and monads: eliminating abstraction overhead from generic code

### 2005-04-10 paper/metamonads.tex
simple correction

That does not seem like much of an improvement. With the help of
camlp4 pre-processor, we introduce the |mdo|-notation (cite XXX),
patterned after the |do|-notation of Haskell. The function
|param_code4|, written in the |mdo|-notation, is equivalent to
|param_code3| -- in fact, the camlp4 preprocessor will convert the
former into the latter. And yet, |param_code4| looks far more
conventional, as if it were indeed in direct style.

@@

Note that the monad is similar to the one used in \cite{KiselyovTaha}.
However, the latter work used only |retN| of all monadic operations,
and used fixpoints (for performing iterations at generation time).
In this paper we do not use monadic fixpoints (because the generator
is not recursive) but we make extensive use of monadic operations for
generating conditional and looping operations.

>>>>

That does not seem like much of an improvement. With the help of
camlp4 pre-processor, we introduce the |mdo|-notation \cite{metamonadsURL},
patterned after the |do|-notation of Haskell. The function
|param_code4|, written in the |mdo|-notation, is equivalent to
|param_code3| -- in fact, the camlp4 preprocessor will convert the
former into the latter. And yet, |param_code4| looks far more
conventional, as if it were indeed in direct style.

@@

The monad in this paper is similar to the one used in \cite{KiselyovTaha}.
However, the latter work used only |retN| of all monadic operations,
and used fixpoints (for performing iterations at generation time).
In this paper we do not use monadic fixpoints (because the generator
is not recursive) but we make extensive use of monadic operations for
generating conditional and looping operations.
